---
title: "HW4_Yun_Young"
output: html_document
---


**Problem #3**
The focus of the EDA stage of an analysis includes, according to Roger Peng, "identifying relationships between variables that are particularly interesting or unexpected, checking to see if there is any evidence for or against a stated hypothesis, checking for problems with the collected data, such as missing data or measurement error, or identifying certain areas where more data need to be collected". However, this is not the final product or for final decision. At this stage, it is more important to examine the data quickly in order to make decisions about what to do next just like "editing room" of filmmaking.


**Problem #4**
```{r, echo=FALSE}
library(rJava)
library(xlsx)
library(corrplot)
library(ggplot2)
library(tidyr)
library(dplyr)
library(grid)
library(gridExtra)

##4
prob4_data1 <- read.xlsx("C:/Users/young/Desktop/R/STAT_5014_homework/04_projecting_knowledge_plots/HW4_data.xlsx", sheetIndex = 1)


##4.1 binds summary of each column and store in summary_comb
summary_comb <- rbind(summary(prob4_data1$block), summary(prob4_data1$depth),
                      summary(prob4_data1$phosphate))
rownames(summary_comb) <- c("block", "depth", "phosphate")

summary_comb


##4.2 gives structure of the data
str(prob4_data1)


##4.3 create various multipanel plots.
par(mfrow=c(1,3))
boxplot(depth~block, prob4_data1, main="Boxplot of depth ~ block")
boxplot(phosphate~block, prob4_data1, main="Boxplot of phosphate ~ block")
plot(prob4_data1$depth, prob4_data1$phosphate, main="Scatterplot of depth vs. phosphate")

print("following is the multipanel plot of depth vs. phosphate by blcok")


for(i in 1:13) #for-loop to examine relation b/w depth and phosphate by the block. 
{
  if (i %in% prob4_data1$block) #skips the block if that block number does not exist
  {
    f <- ggplot(filter(prob4_data1, block == i), aes(depth, phosphate)) + geom_jitter()
    assign(paste("f", i, sep = ""), f)
  }
  
}
grid.arrange(f1, f4, f5, f6, f7, f10, f11, f13, nrow=2, ncol=4) #arrange graphs together



##4.4 correlation plots. This plot creates correlation of the data by color and circle
corTable <- cor(prob4_data1)
corTable
corrplot(corTable, method = "circle", main = "correlation plot by circle")

#4.5
print("Considering the summary statistics and the plots, we need to label columns correctly and descriptively in order to work with plots and summary statistics that read column names")


```



**Problem 5**
```{r, echo=FALSE}
##This code creates 3D scatter plot of prob_4data1. This is great because the graphs analyzed in #4 can be observed altogether in one space.

library(ggplot2)
library(plotly)
library(scatterplot3d)

print("following is 3D scatterplot of prob_4data1 by block, depth, phosphate")

scatterplot3d(prob4_data1$block, prob4_data1$depth, prob4_data1$phosphate, main="3D Scatter Plot", xlab = "Block", ylab = "Depth", zlab = "Phosphate")

```

