---
title: "HW5_Yun_Young"
output: html_document
---

**Problem 3**
What are you thoughts for what makes a good figure?
I think that a good figure should be able to present relationship between variables with clear axis and be easy to recognize.

**Problem 4**

4.a
```{r}
###This code creates a function that counts proportion of success by summing up the input and dividing by the length.
success <- function(x)
{
  sum(x)/length(x)
}
```

4.b
```{r}
#store data as follows
set.seed(12345)
P4b_data <- matrix(rbinom(10, 1, prob = (30:39)/100), nrow = 10, ncol = 10)

```

4.c
```{r, echo=FALSE}
#compute the proportion of success in P4b_data by column and then by row using apply function and by specifying 1 or 2 for column or rows.
#The proportion of success is the same across column and row. The random draws were all identical.

byColumn<-apply(P4b_data, 2, FUN = success)
byRows<-apply(P4b_data, 1, FUN = success)

 xy<- rbind(byColumn, byRows)
knitr::kable(xy, caption="summary of proportion of success by col and row")

```

4.d
```{r}
#create function whose input is a probability and output is a vector whose elements are the outcomes of 10 flips of a coin. Then, use sapply to generate 10 coin flips for each probability.
flipCoin <- function(p)
{
  rbinom(10, 1, p)
}

prob <- (30:39)/100
P4b_data <- sapply(prob, flipCoin)

colnames(P4b_data)<-c("Draw_1", "Draw_2", "Draw_3", "Draw_4","Draw_5","Draw_6","Draw_7","Draw_8","Draw_9","Draw_10")

knitr::kable(P4b_data, caption="10 randomly generated coin filps of 10")

```

**Problem #5**
```{r, echo=FALSE}
###This code cleans the data by filtering by starch and creates scatterplot of strength vs. thickness by starch in the starchData and also create boxplots comparing strength and thickness by starch, and fit multiple graphs in two panels using par(mforw).

library(tidyr)
library(dplyr)

url<-"http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat"
starchData <- read.table(url, header=T, skip=0, fill=T, stringsAsFactors = F)

starch_CA <- filter(starchData, starch == "CA")
starch_CO <- filter(starchData, starch == "CO")
starch_PO <- filter(starchData, starch == "PO")


par(mfrow=c(1,3))
plot(starch_CA$thickness, starch_CA$strength, main = "strength vs. thickness of CA")
plot(starch_CO$thickness, starch_CO$strength, main = "strength vs. thickness of CO")
plot(starch_PO$thickness, starch_PO$strength, main = "strength vs. thickness of PO")

par(mfrow=c(1,2))
boxplot(strength~starch, starchData, main = "strength by starch")
boxplot(thickness~starch, starchData, main = "thickness by starch")


```


**Problem #6**

6.A Get and import a database of US cities and states.
```{r, echo = FALSE}
####This code reads in data, using fread() and puts missing states into the states variable and prints out some of its element using head() to show what the data looks like. 

library(data.table)

states <- fread("./us_cities_and_states/states.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))

states_missing <- matrix(c("Arkansas", "Alabama", "Arizona", "AK", "AL", "AZ"),nrow=3, ncol=2)
colnames(states_missing)<-c("V2", "V4")
states <- rbind(states, states_missing)

cities <- fread(input = "./us_cities_and_states/cities.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))
#can you figure out how to limit this to the 50? 
###Yes! Add the following: nrows = 50


head(states)
head(cities)



```

6.B Create a summary table of the number of cities included by state.
```{r, echo=FALSE}
###The states in cities column are unlisted, put into table and stored. By doing this, we obtain frequency of the states in the cities column.

citycounts <- as.data.frame(table(unlist(cities$V4)))

colnames(citycounts) <- c("State", "CityCount")

citycounts<- citycounts[2:52,1:2]
citycounts<- citycounts[-11,1:2]


knitr::kable(citycounts, caption="City counts by State")

```

Part c. Create a function that counts the number of occurances of a letter in a string.
```{r}
###This code creates 2 functions that counts letters and uses 'sapply' to generate counts for each of the states. The first function, countLetter, counts the number of occurances of a given letter in a given string. The second function, counts, counts the occurrences of letters a~z in a given string using for-loop. Lastly, using the 'sapply' function counts the occurrences of letters for each state in state data, and name the column with letters.

countLetter <- function(letter, state)
{
  state2 <- gsub(letter,"",state)
  return (nchar(state) - nchar(state2))
}


counts <- function(state)
{
  state <- tolower(state)
  Ocurrence <- vector('numeric')
  for(i in 1:26)
  {
    Ocurrence <- combine(Ocurrence, countLetter(letters[i], state))
  }
  return (Ocurrence)
}


letter_count <- t(sapply(states$V2, counts))
colnames(letter_count) <- c(letters[1:26])
```

Part d. Create 2 maps to finalize this. Map 1 should be colored by count of cities on our list within the state. Map 2 should highlight only those states that have more than 3 occurances of ANY letter in thier name.
```{r}
####This code creates two graphics of the United States, using ggplot,in which the states with different citycounts are drawn and with 3 or more recurring letters are drawn. The first one counts the citycounts adds an lower case column of state names and put into graph using ggplot. The second map with 3 or more recurring letters is done by creating a variable called letter_count_three that counts if the state name has more than 3 recurring letters in it by for-looping once to go through letters a~z, and once again to go through 50 states, and filling the variable with 'TRUE' if the state had more than or equal to 3 recurring letters

library(ggplot2)
library(fiftystater)

citycounts <- data.frame(states = tolower(states$V2), citycounts)
citycounts <- select(citycounts, states, CityCount)


#Draw first map
f <- ggplot(citycounts, aes(map_id = states)) +
  geom_map(aes(fill = CityCount), map = fifty_states) +
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "") +
  theme(legend.position = "bottom", panel.background = element_blank())
f


letter_count_three <- select(states, V2) %>% mutate(countGreaterThanThree = NA)

for(i in 1:47)
{
  for(j in 1:26)
  {
   if(letter_count[i, j] >= 3)
   letter_count_three[i, 2] <- TRUE
  }
}

letterCounts <- data.frame(state = tolower(states$V2), letter_count_three)


#Draw second map
p <- ggplot(letterCounts, aes(map_id = state)) +
  geom_map(aes(fill = countGreaterThanThree), map = fifty_states) +
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "") +
  theme(legend.position = "bottom", panel.background = element_blank())
p

```