---
title: "HW5_Yun_Young"
output: html_document
---

**Problem 3**
What are you thoughts for what makes a good figure?
I think that a good figure should be able to present relationship between variables with clear axis and be easy to recognize.

**Problem 4**

4.a
```{r}
#create a function that counts proportion of success by summing up the input and dividing by the length.
success <- function(x)
{
  sum(x)/length(x)
}

```
4.b
```{r}
#store data as follows
set.seed(12345)
P4b_data <- matrix(rbinom(10, 1, prob = (30:39)/100), nrow = 10, ncol = 10)

```

4.c

```{r}
#compute the proportion of success in P4b_data by column and then by row
apply(P4b_data, 2, FUN = success)
apply(P4b_data, 1, FUN = success)

#The proportion of success is the same across column and row. The random draws were all identical.
```

4.d
```{r}
#create function whose input is a probability and output is a vector whose elements are the outcomes of 10 flips of a coin. Then, use sapply to generate 10 coin flips for each probability.
flipCoin <- function(p)
{
  rbinom(10, 1, p)
}

prob <- (30:39)/100
P4b_data <- sapply(prob, flipCoin)
P4b_data

```

**Problem #5**
```{r}
###This code creates scatterplot and boxplot of the data.

library(tidyr)
library(dplyr)

url<-"http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat"
starchData <- read.table(url, header=T, skip=0, fill=T, stringsAsFactors = F)

#filter columns by starch
starch_CA <- filter(starchData, starch == "CA")
starch_CO <- filter(starchData, starch == "CO")
starch_PO <- filter(starchData, starch == "PO")

#create scatterplot of strength vs. thickness by starch
par(mfrow=c(1,3))
plot(starch_CA$thickness, starch_CA$strength, main = "strength vs. thickness of CA")
plot(starch_CO$thickness, starch_CO$strength, main = "strength vs. thickness of CO")
plot(starch_PO$thickness, starch_PO$strength, main = "strength vs. thickness of PO")

#create boxplots comparing strength and thickness by starch.
par(mfrow=c(1,2))
boxplot(strength~starch, starchData, main = "strength by starch")
boxplot(thickness~starch, starchData, main = "thickness by starch")


```


**Problem #6**

6.A Get and import a database of US cities and states.
```{r}
#read in data.
library(data.table)

states <- fread("./us_cities_and_states/states.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))
cities <- fread(input = "./us_cities_and_states/cities.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))

#can you figure out how to limit this to the 50? 
###Yes! Add the following: nrows = 50


```

6.B Create a summary table of the number of cities included by state.
```{r}
###The states in cities column are unlisted, put into table and stored. By doing this, we obtain frequency of the states in the cities column.

citycounts <- as.data.frame(table(unlist(cities$V4)))

colnames(citycounts) <- c("State", "City Count")

citycounts

```

Part c. Create a function that counts the number of occurances of a letter in a string.
```{r}
###This code creates 2 functions that counts letters and uses 'sapply' to generate counts for each of the states.


#This function counts the number of occurances of a given letter in a given string.
countLetter <- function(letter, state)
{
  state2 <- gsub(letter,"",state)
  return (nchar(state) - nchar(state2))
}

#counts occurrences of letters a~z in a given string using for-loop.
counts <- function(state)
{
  state <- tolower(state)
  Ocurrence <- vector('numeric')
  for(i in 1:26)
  {
    Ocurrence <- combine(Ocurrence, countLetter(letters[i], state))
  }
  return (Ocurrence)
}

#counts the occurrences of letters for each state, and name the column with letters
letter_count <- t(sapply(states$V2, counts))
colnames(letter_count) <- c(letters[1:26])
```

```{r}
####This code creates a graphic of the United States, using ggplot,  in which the states with 3 or more recurring letters are colored.

library(ggplot2)
library(fiftystater)

#creates a data.frame with state names and a blank column that will have 'TRUE' value if the states name has more than or equal to 3 recurring letters.

letter_count_three <- select(states, V2) %>% mutate(countGreaterThanThree = NA)


#for-loops once to go through letters a~z, and once again to go through 50 states, and fills the variable with 'TRUE' if the state had more than or equal to 3 recurring letters
for(i in 1:47)
{
  for(j in 1:26)
  {
   if(letter_count[i, j] >= 3)
   letter_count_three[i, 2] <- TRUE
  }
}

#puts the above variable into data.frame, adding a column with small case state names.
letterCounts <- data.frame(state = tolower(states$V2), letter_count_three)


#uses ggplot to color the maps according to the column 'countGreaterThanTree'
p <- ggplot(letterCounts, aes(map_id = state)) +
  geom_map(aes(fill = countGreaterThanThree), map = fifty_states) +
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "") +
  theme(legend.position = "bottom", panel.background = element_blank())
p

```