---
title: "HW2_Yun_Young"
output: html_document
---
```{r pressure, echo=FALSE}
#load relevant pacakges
library(tidyverse)
library(beeswarm)
library(stargazer)
library(data.table)
library(lubridate)
library(readr)

```

**Problem 1**
Completed "R Programming E" lesson parts 4-7, 12 and"Getting and Cleaning Data" lessons parts 1-4.
**Problem 2**
Read through GitHub Chapters 1 and 2.Part A, B, C completed.  
My repo set address on GitHub: <https://github.com/stevewalsh124/STAT_5014.git>

**Problem 3**
Created R Markdown file at the assigned location.  

**Problem#4**
Version Control is a great back-up tool to store data as it captures different versions of the file. Having different files in development can allow you to experiment more freely and makes it easy to track down a mistake. Furthermore, users can easily compare different versions of files to track slight differences.


**Problem#5 Sensory Data Analysis**
```{r pressure, echo=FALSE}
#save url and read it into a variable
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
Sensory_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    
#skip a row to get rid of irrelevant info.
Sensory_tidy<-Sensory_raw[-1,]

#We are going to divide the data into 2 parts
#First part: select observations that has 1,2,3,..., or 10 in column 1, and rename the first column as Item.
Sensory_tidy_a<-filter(.data = Sensory_tidy,V1 %in% 1:10) %>%
                    rename(Item=V1,V1=V2,V2=V3,V3=V4,V4=V5,V5=V6)

#Second part: select observations that are not 1 through 10, and create a column 'Item' that assgin item numbers to observation
Sensory_tidy_b<-filter(.data = Sensory_tidy,!(V1 %in% 1:10)) %>%
                    mutate(Item=rep(as.character(1:10),each=2)) %>%
                    mutate(V1=as.numeric(V1)) %>%
                    select(c(Item,V1:V5))

#Now, combine rows for our 2 datas
Sensory_tidy<-bind_rows(Sensory_tidy_a,Sensory_tidy_b)

#set colnames with more distinctive names
colnames(Sensory_tidy)<-c("Item",paste("Person",1:5,sep="_"))

#gather columns so that we have the variable in one column
#remove redundunt description 'person', then arrange by item
Sensory_tidy<-Sensory_tidy %>%  gather(Person,value,Person_1:Person_5) %>%  
        mutate(Person = gsub("Person_","",Person)) %>%
        arrange(Item)

#gives a summary of data in a table
 knitr::kable(summary(Sensory_tidy), caption="Sensory data summary")
 
```


      
**Problem#5 LongJump Analysis**

```{r}

#save url and read it into a variable
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat"
LongJump_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    
#Set colnames by repeating V1,V2 four times. 
colnames(LongJump_raw)<-rep(c("V1","V2"),4)

#combine the same columns together
LongJump_tidy<-rbind(LongJump_raw[,1:2],LongJump_raw[,3:4], LongJump_raw[,5:6],LongJump_raw[,7:8])

#filter NAs in column1, create descriptive columns for Year, and discard redundunt columns.
LongJump_tidy<-LongJump_tidy %>%  
        filter(!(is.na(V1))) %>%
        mutate(YearCode=V1, Year=V1+1900, dist=V2) %>%
        select(-V1,-V2)

#gives a summary of data in a table
knitr::kable(summary(LongJump_tidy), caption="Long Jump data summary")

```

**Problem#5 BrainBody Weight**
```{r}

#save url and read it into a variable
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat"
BrainBody_raw<-read.table(url, header=T, skip=0, fill=T, stringsAsFactors = F)
 
#Set colnames to equal Brain and Body repeatedly for three times
colnames(BrainBody_raw)<-rep(c("Brain","Body"),3)

#Combine columns that have same values
BrainBody_tidy <- rbind(BrainBody_raw[,1:2], BrainBody_raw[,3:4], BrainBody_raw[,5:6])

#filter out NAs in Brain column
BrainBody_tidy <- BrainBody_tidy %>% filter(!(is.na(Brain)))

#gives a summary of data in a table
knitr::kable(summary(BrainBody_tidy), caption="Brain/Body weight data summary")
```


**Problem#5 Tomato analysis**
```{r}
#save url and read it into a variable
url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat"
Tomato_raw<-read.table(url, header=F, skip=2, fill=T, stringsAsFactors = F, comment.char = "")

#separate each column 2,3,4 into three distinct columns so that we have one value at a time
#takes out a comma from entry in C10000_3
#gathers multiple but same variable columns into one.
#Create a copy of column1 and take out 'C' from Column Clone
#Remove \\# expression from Variety column
#separate Clone into 2 columns
#select the columns we need
#arrange by Variety
Tomato_tidy<-Tomato_raw %>%  
        separate(V2,into=paste("C10000",1:3,sep="_"),sep=",",remove=T, extra="merge")  %>%
        separate(V3,into=paste("C20000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        separate(V4,into=paste("C30000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        mutate(C10000_3=gsub(",","",C10000_3))%>% 
        gather(Clone,value,C10000_1:C30000_3) %>% 
        mutate(Variety=V1, Clone=gsub("C","",Clone))%>%
        mutate(Variety=gsub("\\\\#"," ",Variety)) %>%
        separate(Clone,into = c("Clone","Replicate")) %>%
        select(Variety, Clone,value) %>%
        arrange(Variety)

#gives a summary of data in a table
knitr::kable(summary(Tomato_tidy), caption="Tomato data summary")
```


**Problem#6**

```{r}

library(swirl)
# Specifies Path to data
.datapath <- file.path(path.package('swirl'), 'Courses','R_Programming_E', 'Looking_at_Data',
                      'plant-data.txt')

#Save data into variable
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")


#Select interested columns, filters NAs, and create a column with statistic that combines pH min and max.
plants <- select(plants, Accepted.Symbol, Scientific.Name, Foliage.Color, pH..Minimum., pH..Maximum.)%>%filter(!is.na(Foliage.Color))%>%filter(!is.na(pH..Minimum.))%>% mutate(pH.Ratio= pH..Minimum./pH..Maximum.)

#create linear model using lm()
fit <- lm(pH.Ratio~Foliage.Color , data=plants)

#gives summary tableof plants
knitr::kable(summary(plants), caption="plants data summary")

#generate anova analysis
anova(fit)
```


**Problem#7**

```{r}
#This gives defect, and inspection details
Car_Gebreken_select <- fread(input = "Open_Data_RDW__Gebreken.csv", header = T, select=c(1,6), showProgress=F)

#This gives license plate, and inspection date, and defect code
Car_Geconstat_select <- fread(input = "Open_Data_RDW__Geconstateerde_Gebreken.csv", header=T, select=c(1,3,5),showProgress=F)

#
Car_Geconstat_select_2017 <- Car_Geconstat_select[grep("2017",Car_Geconstat_select$"Meld datum door keuringsinstantie"),]

#this has the license plate, make and model of vehicle, and date. fread() returns unknown error, so I used read.csv
Car_Person_raw <- read.csv("Personenauto_basisdata.csv",stringsAsFactors = F, nrow=10000, header=T) 
Car_Person_select <- select(Car_Person_raw, c(1,3,5))
Car_Person_select_2017 <- Car_Person_select[grep("2017", Car_Person_select$"Datum.tenaamstelling"),]

#The data files are too big and everytime I call on any function to modify or just to see the data R crashes...
```

